---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---

`gzmem` : Better gz in memory compression/decompression

A partial resurrection of `Rcompression` for [this](http://stackoverflow.com/q/39707388/1457051).

The following functions are implemented:

- `mem_compress`:	Compress a raw vector using gz compression
- `mem_inflate`:	Inflate a raw vector that was gz compressed

### TODO

- [ ] Rewrite in Rcpp
- [ ] Make inflation dynamic vs relying on guessed bufffer size

### Installation

```{r eval=FALSE}
devtools::install_git("https://gitlab.com/hrbrmstr/gzmem.git")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r echo=TRUE, message=FALSE, warning=FALSE, error=FALSE}
library(gzmem)
library(magrittr)

# current verison
packageVersion("gzmem")

text <- "Hey, the room is getting smaller. No, it's not. *He's* getting *bigger*!"

text %>% 
  charToRaw() %>% 
  mem_compress(format = "gzip")

text %>% 
  charToRaw() %>% 
  mem_compress(format = "gzip") %>% 
  mem_inflate(format = "gzip", 1024) %>% 
  rawToChar()
```

### Test Results

```{r echo=TRUE, message=FALSE, warning=FALSE, error=FALSE}
library(gzmem)
library(testthat)

date()

test_dir("tests/")
```

