---
output: rmarkdown::github_document
---

`gzmem` : Better in memory compression/decompression

A partial resurrection of `Rcompression` for [this](http://stackoverflow.com/q/39707388/1457051).

The following functions are implemented:

- `mem_compress`:	Compress a raw vector
- `mem_inflate`:	Inflate a raw vector compressed

### TODO

- [ ] Rewrite in Rcpp
- [ ] Make inflation dynamic vs relying on guessed bufffer size

### Installation

```{r eval=FALSE}
devtools::install_git("https://gitlab.com/hrbrmstr/gzmem.git")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

```{r echo=TRUE, message=FALSE, warning=FALSE, error=FALSE}
library(gzmem)
library(magrittr)

# current verison
packageVersion("gzmem")
```

### Usage

This package contains functions to compress and decompress raw vectors in R using the zlib library (https://zlib.net/). 

It supports 3 different formats: gzip, zlib and raw. These formats all use the deflate algorithm to compress the data (https://en.wikipedia.org/wiki/DEFLATE), but differ in the headers and footers they wrap around the deflate compressed data:

- gzip has a 10 byte header and an 8 byte footer around the compressed data.
- zlib has a 2 byte header and a 4 byte footer around the compressed data.
- raw has no header or footer, and so is just the deflate compressed data.

For example:

```{r}
text <- "Hey, the room is getting smaller. No, it's not. *He's* getting *bigger*!"
```

Shows the following differences between all 3 formats:

```{r}
gzip <- text %>% 
  charToRaw() %>% 
  mem_compress(format = "gzip")
```
```{r,echo=F}
gzip
```
```{r}
zlib <- text %>% 
  charToRaw() %>% 
  mem_compress(format = "zlib")
```
```{r, echo=F}
zlib
```
```{r}
raw <- text %>% 
  charToRaw() %>% 
  mem_compress(format = "raw")
```
```{r, echo=F}
raw
```

These can then be decompressed by selecting the appropriate format:

```{r}
gzip %>%
  mem_inflate(format = "gzip", 1024) %>% 
  rawToChar()
```




### Test Results

```{r echo=TRUE, message=FALSE, warning=FALSE, error=FALSE}
library(gzmem)
library(testthat)

date()

test_dir("tests/")
```

